ecmlpkdd2016

### 2016-08-28 main_train_without_stacking.Rmd
update

# 2Folds stacking
```{r}
# Number of stack
NUM_STACK = 11

## config
N_FOLD = 5
ETA = 0.3
EARLY_STOP = 25
LAMBDA = 30
SUB_SAMPLE = 0.95
MAX_DEPTH = 3
MODEL_ID = 7

@@

### stacking vectors
counter = 0
for (i in list.files("Documents/github/ecmlpkdd2016_final/cache/2014-1-6_vector/")){
  if (counter == NUM_STACK){
    break
  }
  print(i)
  tmp_f = read_csv(paste0("Documents/github/ecmlpkdd2016_final/cache/2014-1-6_vector/",i))
  names(tmp_f) = c("USER_ID", i)
  user_2014_month_1_6 = merge(user_2014_month_1_6, tmp_f, by= "USER_ID", all.x=T)
  counter = counter+1
}
counter = 0
for (i in list.files("Documents/github/ecmlpkdd2016_final/cache/2014-7-12_vector/")){
  if (counter == NUM_STACK){
    break
  }  
  print(i)
  tmp_f = read_csv(paste0("Documents/github/ecmlpkdd2016_final/cache/2014-7-12_vector/",i))
  names(tmp_f) = c("USER_ID", i)
  user_2014_month_7_12 = merge(user_2014_month_7_12, tmp_f, by= "USER_ID", all.x = T)
  counter = counter+1
}

>>>>

# 2Folds stacking
```{r}
## config
N_FOLD = 5
ETA = 0.3
EARLY_STOP = 25
LAMBDA = 30
SUB_SAMPLE = 0.95
MAX_DEPTH = 3
MODEL_ID = 7

@@
